\documentclass[a4paper]{proc}

\title{18 month progress report}
\author{Sherman Ip \quad Statistics \quad University of Warwick \quad March 31, 2017}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage{natbib}
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}

\DeclareMathOperator{\expfamily}{ExpFamily}
\DeclareMathOperator{\expectation}{\mathbb{E}}
\DeclareMathOperator{\variance}{\mathbb{V}ar}
\DeclareMathOperator{\cov}{\mathbb{C}ov}
\DeclareMathOperator{\corr}{\mathbb{C}orr}
\DeclareMathOperator{\bernoulli}{Bernoulli}
\DeclareMathOperator{\betaDist}{Beta}
\DeclareMathOperator{\dirichlet}{Dir}
\DeclareMathOperator{\bin}{Bin}
\DeclareMathOperator{\MN}{Multinomial}
\DeclareMathOperator{\prob}{\mathbb{P}}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\normal}{N}
\DeclareMathOperator{\gammaDist}{Gamma}
\DeclareMathOperator{\poisson}{Poisson}

\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\euler}{\mathrm{e}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\T}{^\textup{T}}
\newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
\newcommand{\BIC}{\textup{BIC}}

\newcommand{\vect}[1]{\mathbf{#1}}
\newcommand{\vectGreek}[1]{\boldsymbol{#1}}
\newcommand{\matr}[1]{\mathsf{#1}}

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
3D printing, or additive layer manufacturing, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.  Recently it has been commercialised and has served purposes in the medical field and engineering. The need for detecting defects from 3D printing is required in order to do quality control, especially if the 3D printed object is used for something critical for example body parts. 

X-ray computed tomography (CT) scans can be used to take images of a rotating 3D printed sample to obtain images at multiple angles. These x-ray images then can be combined to form a 3D projection and the detection of defects can start. However due to the random nature of x-ray photons in its production in an x-ray tube and attenuation, sources of error or noise is introduced. In order to do defect detection in a statistical manner, sources of error must be considered.

A mini-project on this topic was completed at 12 months of the PhD \cite{ip2016inside}. The main aim of that project was to conduct exploratory data analysis on a dataset of 100 images of an x-ray CT scan of a stationary 3D printed cuboid. Linear regressions were used to model the relationship between the variance and the mean greyvalue of each pixel. Separately latent variable models were fitted (or at least attempted) on the scans, such as PCA, factor analysis and the compound Poisson, to find sources of variance.

After the mini-project, the main aims during the PhD was to extend the mini-project by developing a statistic to aid in defect detection while considering the randomness of photons. Another aim was to build a model for the noise.

\bibliographystyle{unsrt}
\bibliography{../bib}

\end{document}
